Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles

### 2014-07-24 paper/paper.tex
Add some more to the paper

\begin{abstract}
\hl{Because there are always more molecules to test than time}, there is a need to quickly be able to rule out structures that are unsuitable for further research. The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations. By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested. These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculation.
\end{abstract}

@@

Density functional theory calculations have been used extensively to be able to predict the properties at a nice medium between the accuracy of \emph{ab inito} and the speed of semi empirical methods. Unfortunately, while they are faster than \emph{ab inito} calculations, DFT calculations still take a lot longer than to be desired. This problem is compounded when much of the interest in computational chemistry is being able to test molecules more quickly than could be done in the lab.

>>>>

\begin{abstract}
\hl{Because there are always more molecules to test than time}, there is a need to quickly be able to rule out structures that are unsuitable for further research. The method presented in this paper takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations. By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested. These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculation.
\end{abstract}

@@

Density functional theory calculations have been used extensively to be able to predict the properties at a nice medium between the accuracy of \emph{ab inito} and the speed of semi empirical methods. Unfortunately, while they are faster than \emph{ab inito} calculations, DFT calculations still take a lot longer than to be desired. This problem is compounded when one of the of the interests in computational chemistry is being able to test molecules more quickly than could be done in the lab.
